The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step

### 2017-03-27 Moving temporal window - HESS/template.tex
HESS paper under work.

	\begin{itemize}
		\item The spatial windows, which are the domains on which predictors are compared. There is a spatial window specific to each level of analogy. It will thus differ between circulation and moisture variables.
		\item The optimal number of analog situations for every level of analogy.
	\end{itemize}

@@

	%TODO: on the CP or the VP ? -> test on VP before/after recalib

@@

	\subsection{Inflation of the precipitation archive}
	\label{sec:archive_reduction}

	%TODO: do calculations of the conequence of the archive reduction
	%TODO: rewrite this section

	Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected. However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.

	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect. \ref{sec:mtw}) was assessed with the original method without MTW. Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered. The AM parameters were calibrated on the original archive (see resulting analogue numbers in Fig. \ref{fig:analog_nb}) and were used thereafter.

	The impact of the archive reduction can be seen in Fig. \ref{fig:plots_CRPS_2Z} for the 2Z method and in Fig. \ref{fig:plots_CRPS_2Z-2MI} for the 2Z-2MI method. As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change. This loss was globally significant, with up to \textendash 1.89 points (\% of CRPS) for Visp and the 2Z method.

	The MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}, Sect. \ref{sec:influence_scores}). Moreover, it required no additional predictor. With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated (considering a 25 year archive of sub-daily data; the difference could be higher with a shorter archive). It was in this case of the same magnitude as if the length of the archive doubled. Note, that despite the number of candidate situations being 4 times as many, the gains seem to be lower than for a quadrupled archive length. The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period. Moreover, high correlations between sub-daily circulation patterns are expected. The MTW, therefore, did not create 4 times as many independent data, but the increase in information was nevertheless substantial. In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset. In contrast, reducing the MTW to a 12-hour time step might reduce redundancy in the archive, but might also reduce the chance of finding better analogue situations, as circulation patterns can evolve substantially in 12~hours.

	Moreover, in a transient climate, an eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past and increase the relevance of using a more recent and shorter archive rather than a long one. In such cases, the archive inflation brought by the MTW is also relevant.

@@

	It would be profitable to be able to apply the MTW to a longer archive (here, 1961\textendash 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf. previous section). Therefore, in order to reconstruct a longer archive of moving 24h totals, two simple disaggregation approaches of the daily precipitation time series were assessed.

@@

	The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative variables during the reconstruction procedure. Data from the NCEP/NCAR reanalysis 1 (Sect. \ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\textdegree). Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point. The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series over the period 1982\textendash 2007. Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.

	The reconstructed time series cover the full period. However, they were first assessed using the MTW on the reduced period in order be comparable with the real sub-daily precipitation time series, and thus to evaluate their relevance and the possible loss in performance score.

	When using the first reconstructed time series based on the proportional distribution (see Sect. \ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW.

	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first. The results are illustrated this time for the Zermatt station. Among the considered moisture variables (see Sect. \ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of \textendash 6~h. xx presents the CRPS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.

	The two simple methods assessed to reconstruct precipitation archives (Sect. \ref{sec:reconstruction}) did not result in valuable outputs (Sect. \ref{sec:reconstruction_results}). Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the precipitation archives. A slight improvement could be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it was still relatively small, and most of the benefit of the MTW was lost. A more recent reanalysis archive with more accurate moisture variables might produce better proxies.

@@

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig03.pdf}
		\caption{Performance score (CRPS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e. 1961\textendash 2008; (yellow) the reduced archive, i.e. 1982\textendash 2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
		\label{fig:plots_CRPS_2Z}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig04.pdf}
		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the analogue method with a second level with the moisture variables.}
		\label{fig:plots_CRPS_2Z-2MI}
	\end{figure}

@@

	\begin{figure}[htb]
	\includegraphics[width=7.5cm]{fig12.pdf}
	\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z) and the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
	\label{fig:analog_nb}
	\end{figure}

>>>>

	\begin{itemize}
		\item The spatial windows, which are the domains on which predictors are compared. There is a spatial window specific to each level of analogy. It will thus differ between circulation and moisture variables.
		\item The optimal number of analogue situations for every level of analogy.
	\end{itemize}

@@

@@

	\subsection{Inflation of the archive}
	\label{sec:archive_reduction}

	Since sub-daily precipitation time series are often available on a shorter period than daily ones, this implies a reduction of the archive length at disposal for the search of analogue situations. This usually has a negative consequence on the skill of precipitation prediction. The role of the archive length has been assessed on the ERA-20C dataset and is presented in Fig. \ref{fig:plots_archive_length} for both 2Z and 2Z-2MI methods, using the conventional approach (24h windows). As expected, the performance of the method globally increases with the length of the archive. The best performances are found with a 44 yr archive, corresponding to the period 1961--2010, minus the 6 years of independant data set apart for validation. This addition of 21~yr of archive to the original 23~yr results in an improvement of both 2Z and 2Z-2MI methods that is of the same order of magnitude as the introduction of a 6h-MTW (Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}). The 3h-MTW resulted in similar performance for the 2Z method and slight improvements for the 2Z-2MI method.

	As the MTW provides additional situations to the pool of possible analogues, it can be seen as an inflation of the archive. With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length (to meet the length of the subdaily precipitation archive) was compensated. A 6h-MTW brought gains of the same magnitude as if the length of the archive doubled. Note, that despite the number of candidate situations being 4 times as many, the gains seem to be lower than for a quadrupled archive length. The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period. Moreover, high correlations between sub-daily circulation patterns are expected. The MTW, therefore, did not create 4 times as many independent data, but the increase in information was nevertheless substantial.

	Many reanalysis datasets start in the 80s due to availability of satellite data, and are thus more accurate than reanalysis datasets based on conventional data, but provide a shorter archive length. When using such an archive, the MTW approach shows a certain potential to enrich the pool of possible analogues. Moreover, in a transient climate, an eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past and increase the relevance of using a more recent and shorter archive rather than a long one. In such cases, the archive inflation brought by the MTW is also relevant.

@@

	As we saw in Sect. \ref{sec:archive_reduction}, the skills of AMs improve with the length of the archive. It would then be even more profitable to apply the MTW to the longest archive possible, rather than being limited to the period where the sub-daily precipitation data are available. Therefore, in order to reconstruct longer archives of moving 24h totals, disaggregation techniques might be used. Where, two simple disaggregation approaches of the daily precipitation time series were assessed.

@@

	The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative variables during the reconstruction procedure. Data from the NCEP/NCAR reanalysis 1 (Sect. \ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\textdegree). Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point. The best proxy variable, which was precipitable water, was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series. Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.

	These two simple methods assessed to reconstruct precipitation archives did not result in valuable outputs (results not shown). Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the precipitation archives. A slight improvement could be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it was still relatively small, and most of the benefit of the MTW was lost. Another reanalysis dataset with more accurate moisture variables might produce better proxies.

@@

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig03.pdf}
		\caption{Change in performance score (CRPS -- lower is better) of the 2Z method at the different stations for MTW of varying time steps relatively to the conventional approach (24h). Results are provided for ERA-20C on (a) the CP and (b) the VP, as well as for MERRA-2 on (c) the CP and (d) the VP.}
		\label{fig:plots_CRPS_2Z}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig04.pdf}
		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the 2Z-2MI method.}
		\label{fig:plots_CRPS_2Z-2MI}
	\end{figure}

@@

	\begin{figure}[htb]
		\includegraphics[width=7.5cm]{fig12.pdf}
		\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the (a) 2Z and (b, c) 2Z-2MI methods after recalibration using the MTW.}
		\label{fig:analog_nb}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig13.pdf}
		\caption{Change in performance score (CRPS -- lower is better) of the (a, b) 2Z and (c, d) 2Z-2MI methods at the different stations on the (a, c) CP and (b, d) VP, for an increasing archive length with the conventional approach (24h windows).}
		\label{fig:plots_archive_length}
	\end{figure}
